---
name: Dr Victor
surname: Maus
position: "Senior Researcher"
address: "Welthandelsplatz 1, 1020 Vienna, Austria"
phone: +43 1 31336 6176
www: victor-maus.com
email: "vwmaus1@gmail.com"
twitter: victor_maus
github: vwmaus
orcid: 0000-0002-7385-4723
scholar: wN2LseQAAAAJ&hl
linkedin: victor-maus-083a79191
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

I am a researcher in Geoinformatics and GIScience interested in environmental modeling and monitoring to understand drivers of global environmental change. My research has contributed to new methods for analyzing large satellite image data sets and help better understand the interactions between environment and human activities. I am experienced in IT, software development, management of servers and web services. To support my research, I have developed software and tools to visualize, handle and analyze large volumes of heterogeneous geodata, from statistical surveys to citizen science and satellite earth observations.

# EDUCATION

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD in Earth System Science", "2016", "National Institute for Space Research (INPE)", "São José dos Campos, Brazil",
  "MSc in Computational Modeling", "2011", "Federal University of Juiz de Fora (UFJF)", "Juiz de Fora, Brazil",
  "BSc in Environmental Engineering", "2009", "Franciscan University (UFN)", "Santa Maria, Brazil"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# CURRENT POSITIONS
```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Senior Researcher", "2018-", "Vienna University of Economics and Business (WU)", "Vienna, Austria",
  "Research Scholar", "2016-", "International Institute for Applied Systems Analysis (IIASA)", "Laxenburg, Austria",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# PREVIOUS POSITIONS
```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Research Assistant", "2014-2016", "University of Münster (WWU)", "Münster, Germany",
  "University Lecturer", "2012-2014", "Federal University of Pampa (UNIPAMPA)", "Itaqui, Brazil",
  "Research Assistant", "2011-2012", "National Institute for Space Research (INPE)", "São José dos Campos, Brazil",
    "Research Assistant", "2009-2011", "Federal University of Juiz de Fora (UFJF)", "Juiz de Fora, Brazil"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# FELLOWSHIPS AND AWARDS

# SUPERVISION OF STUDENTS

# TEACHING ACTIVITIES

# INSTITUTIONAL RESPONSIBILITIES

# REVIEWING ACTIVITIES

# PUBLICATIONS

```{r}
library(dplyr)
library(stringr)
bold_author <- function(x){
  res <- lapply(x, function(x) lapply(x, function(y) csl_name(given = y$given, family = str_replace(y$family, "Maus", "boldmaus"))))
  #class(res) <- c("list_of_csl_names", "vctrs_list_of", "vctrs_vctr", "list")
  list_of_csl_names(res)
}
bibliography_entries("./../_bibliography/papers.bib") %>%
  filter(type == "article-journal") %>%
  # mutate(author = bold_author(author)) %>% 
  arrange(desc(issued), issued)
```
